---
title: "T3-CiteScore-2017"
output: html_notebook
---

# Methods

## Data preparation

1. download Cite Score 2017 (version April 2018), published 30 May 2018, format xls, size +/- 17 MB link,
2. sort data based on Publisher's country column, select Indonesia,
3. convert columns with score to number. For unknown reason, original Cite Score data use text format for all columns, including columns with score,
4. rename columns for easy reading in csv format,
5. save as in utf-8 csv format.

## Data analysis

1. basic statistics
2. multivariate statistics

## Individual journal check

1. website
2. article check:

  - sum of article
  - highest cited article
  - lowest cited article
  - etc to be added

```{r}
df = read.csv('prep-data-citescore-ID-Apr-2018.csv')
head(df)
str(df)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r}
# installing and loading libraries

#install.packages('FactoMineR')
#install.packages('factoextra')
#install.packages('tidyverse')
```

```{r}
library('tidyverse')
library('FactoMineR')
library('factoextra')
```


```{r}
# visualization
ggplot(df, aes(x='2017_cs', y='2017_sjr')) + geom_line()
```

